Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-06-01 manuscript.Rmd
Update abstract

abstract: |
  Social mobilization requires effective collective coordination. In recent 
  years, individuals involved in social movements have taken to social media
  platforms to reach broader audiences at rapid speeds. Effective virtual 
  mobilization similarly requires social cohesion and coordination, yet the 
  degree to which virtual mobilization reflects or drives real-world movements
  is unclear. Here, we explore the dynamics of real-world events and social 
  cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear 
  methods cross-recurrence quantification analysis and windowed cross-recurrence
  quantification analysis, we investigate if counts of all daily events, daily 
  positive events, and daily negative events are coupled with social cohesion 
  found in Syrian tweets. Results indicate that virtual social cohesion is 
  coupled with the counts of all and negative events each day but not with 
  counts of positive events. This suggests that virtual mobilization does reflect 
  real-world movements but only for salient, frequent and negative events. We 
  conclude with a discussion of implications and applications of nonlinear 
  methods in political science research.
  <!-- https://tinyurl.com/ybremelq -->

>>>>

abstract: |
  Social mobilization requires effective collective coordination. In recent 
  years, individuals involved in social movements have taken to social media
  platforms to reach broader audiences at rapid speeds. Effective virtual 
  mobilization similarly requires social cohesion and coordination, yet the 
  degree to which virtual mobilization reflects or drives real-world movements
  is unclear. Here, we explore the dynamics of real-world events and social 
  cohesion on Twitter in Syria during the Arab Spring. Using the nonlinear 
  methods cross-recurrence quantification analysis and windowed cross-recurrence
  quantification analysis, we investigate if counts of all daily events, daily 
  positive events, and daily negative events are coupled with social cohesion 
  found in Syrian tweets. Results indicate that virtual social cohesion is 
  coupled with the counts of all and negative events each day but shows a more
  nuanced connection to positive events, only visible when examining finer-grained
  data. This suggests that virtual mobilization does reflect 
  real-world movements, with the strongest connections to the frequency of all
  events and the frequency of negative events. We 
  conclude with a discussion of implications and applications of nonlinear 
  methods in political science research.
  <!-- https://tinyurl.com/ybremelq -->
